Formal Proof of the Relative Consistency of ZF$+\neg$AC with Isabelle/ZF

### 2025-01-08 paper/main copy.tex
updated

\tiny{\url{https://github.com/tarakojo/ZF_notAC/blob/a376fdd7222b5b1fdb7681a1f542521e8805d82e/code/P_Names.thy#L10}}
\begin{isaframe}
\begin{minted}[breaklines]{isabelle}
definition HP_set_succ :: "[i, i] ⇒ i" where 
    "HP_set_succ(a, X) ≡ Pow(X × P) ∩ M"

@@

\begin{isaframe}
\begin{minted}[breaklines]{isabelle}
locale forcing_data_partial = forcing_data + 
    assumes leq_relation_on_P : "leq ∈ Pow(P × P)" 
    and leq_partial_order : "partial_order_on(P, leq)" 
\end{minted}
\end{isaframe}
\tiny{\url{https://github.com/tarakojo/ZF_notAC/blob/a376fdd7222b5b1fdb7681a1f542521e8805d82e/code/Automorphism_Definition.thy#L5}}

@@

definition P_auto where "P_auto ≡ { π ∈ P → P. is_P_auto(π) }" 
\end{minted}
\end{isaframe}
\tiny{\href{https://github.com/tarakojo/ZF_notAC/blob/a376fdd7222b5b1fdb7681a1f542521e8805d82e/code/Automorphism_Definition.thy#L25}{Automorphism\_Definition.thy:25-28}}

>>>>

\noindent{\tiny\url{https://github.com/tarakojo/ZF_notAC/blob/a376fdd7222b5b1fdb7681a1f542521e8805d82e/code/P_Names.thy#L10}}
\begin{isaframe}
\begin{minted}[breaklines]{isabelle}
definition HP_set_succ :: "[i, i] ⇒ i" where 
    "HP_set_succ(a, X) ≡ Pow(X × P) ∩ M"

@@

\begin{isaframe}
\begin{minted}[breaklines]{isabelle}
locale forcing_data_partial = forcing_data + 
    assumes leq_relation_on_P : "leq ∈ Pow(P × P)" 
    and leq_partial_order : "partial_order_on(P, leq)" 
\end{minted}
\end{isaframe}
%\tiny{\url{https://github.com/tarakojo/ZF_notAC/blob/a376fdd7222b5b1fdb7681a1f542521e8805d82e/code/Automorphism_Definition.thy#L5}}

@@

definition P_auto where "P_auto ≡ { π ∈ P → P. is_P_auto(π) }" 
\end{minted}
\end{isaframe}
%\tiny{\href{https://github.com/tarakojo/ZF_notAC/blob/a376fdd7222b5b1fdb7681a1f542521e8805d82e/code/Automorphism_Definition.thy#L25}{Automorphism\_Definition.thy:25-28}}
